Gammapy: A Python package for gamma-ray astronomy

### 2023-08-23 src/ms-review.tex
Clean up imports
Remove split author list

\author{
        {\it Paper Authors} \and
    Axel Donath \inst{\ref{inst:28}} \and
        Régis Terrier \inst{\ref{inst:20}} \and
        Quentin Remy \inst{\ref{inst:17}} \and
        Atreyee Sinha \inst{\ref{inst:15}} \and
        Cosimo Nigro \inst{\ref{inst:24}} \and
        Fabio Pintore \inst{\ref{inst:26}} \and
        Bruno Khélifi \inst{\ref{inst:20}} \and
        Laura Olivera-Nieto \inst{\ref{inst:17}}\and
        Jose Enrique {Ruiz} \inst{\ref{inst:23}} \and
        Kai Brügge \inst{\ref{inst:10},\ref{inst:11}} \and
        Maximilian Linhoff \inst{\ref{inst:11}} \and
        Jose Louis {Contreras} \inst{\ref{inst:15}} \and
        \\
        {\it Coordination Committee}\thanks{Corresponding author:
\href{mailto:GAMMAPY-COORDINATION-L@IN2P3.FR}{GAMMAPY-COORDINATION-L@IN2P3.FR}} \and
        Fabio Acero \inst{\ref{inst:1}} \and
        David Berge \inst{\ref{inst:6}, \ref{inst:7}} \and
        Catherine Boisson \inst{\ref{inst:9}} \and
        Jose Louis {Contreras} \inst{\ref{inst:15}} \and
        Axel Donath \inst{\ref{inst:28}} \and
        Stefan Funk \inst{\ref{inst:19}} \and
        Christopher {van Eldik} \inst{\ref{inst:19}} \and
        Matthias Fü{\ss}ling \inst{\ref{inst:18}} \and
        Jim Hinton \inst{\ref{inst:17}} \and
        Bruno Khélifi \inst{\ref{inst:20}} \and
        Rub{\'e}n L{\'o}pez-Coto \inst{\ref{inst:23}} \and
        Fabio Pintore \inst{\ref{inst:26}} \and
        Régis Terrier \inst{\ref{inst:20}} \and
        Roberta Zanin \inst{\ref{inst:18}} \and
    \\
        {\it Gammapy Project Contributors} \and
        Arnau Aguasca-Cabot \inst{\ref{inst:2}, \ref{inst:3}, \ref{inst:4}, \ref{inst:5}} \and
        Pooja Bhattacharjee \inst{\ref{inst:8}} \and
        Johannes Buchner \inst{\ref{inst:12}} \and
        David {Carreto Fidalgo} \inst{\ref{inst:13}} \and
        Andrew Chen \inst{\ref{inst:14}} \and
        Mathieu {de Bony de Lavergne} \inst{\ref{inst:8}} \and
        José Vinícius {de Miranda Cardoso}\inst{\ref{inst:16}} \and
        Christoph Deil \inst{\ref{inst:17}} \and
        Luca Giunti \inst{\ref{inst:20}} \and
        Léa Jouvin \inst{\ref{inst:32}} \and
        Johannes King \inst{\ref{inst:30}, \ref{inst:17}} \and
        Julien Lefaucheur \inst{\ref{inst:21}, \ref{inst:20}} \and
        Marianne Lemoine-Goumard \inst{\ref{inst:31}} \and
        Jean-Philippe Lenain \inst{\ref{inst:22}} \and
        Lars Mohrmann \inst{\ref{inst:17}} \and
        Daniel Morcuende \inst{\ref{inst:15}} \and
        Sebastian Panny \inst{\ref{inst:25}} \and
        Maxime Regeard \inst{\ref{inst:20}} \and
        Lab Saha \inst{\ref{inst:15}} \and
        Hubert Siejkowski \inst{\ref{inst:27}} \and
        Aneta Siemiginowska \inst{\ref{inst:28}} \and
        Brigitta M. {Sipőcz} \inst{\ref{inst:29}} \and
        Tim Unbehaun \inst{\ref{inst:19}} \and
        Thomas Vuillaume \inst{\ref{inst:8}}
}

@@

\begin{figure}
        \small
        %Added by TeX Support
        %\import{code-examples/generated/}{gp_data}
        \caption{
        Using \code{gammapy.data} to access DL3 level data with a \code{DataStore} object.
        Individual observations can be accessed by their unique integer observation id number.
        The actual events and instrument response functions can be accessed
        as attributes on the \code{Observation} object, such as \code{.events}
        or \code{.aeff} for the effective area information. The output
                of the code example is shown in Figure~\ref{fig:code_example_gp_data}.
    }
        \label{fig*:minted:gp_data}
\end{figure}
%

@@

\begin{figure}
        \small
        %Added by TeX Support
        %\import{code-examples/generated/}{gp_maps}

@@

\subsection{gammapy.datasets}
\label{ssec:gammapy-datasets}
%
\begin{figure}
        \small
        %Added by TeX Support
        %\import{code-examples/generated/}{gp_datasets}
        \caption{
        Using \code{gammapy.datasets} to read existing reduced binned datasets.
        After the different datasets are read from disk they are collected into a
        common \code{Datasets} container. All dataset types have an associated
        name attribute to allow a later access by name in the code. The
        environment variable \code{\$GAMMAPY\_DATA} is automatically resolved
        by \gammapy. The output
                of the code example is shown in Figure~\ref{fig:code_example_gp_datasets}.
    }
        \label{fig*:minted:gp_datasets}
\end{figure}
%
The \code{gammapy.datasets} sub-package contains classes to bundle
together binned data along with the associated models and likelihood function, which
provides an interface to the \code{Fit} class (Sec \ref{sssec:fit}) for
modeling and fitting purposes. Depending upon the type of analysis and the
associated statistic, different types of Datasets are supported. The \code{MapDataset} is
used for combined spectral and morphological (3D) fitting, while spectral 
fitting only can be performed using the \code{SpectrumDataset}.
While the default fit statistics for both of these classes is the \emph{Cash}~\citep{Cash}
statistic, there are other classes which support
analyses where the background is measured from control regions, so called \enquote{off} observations.
Those require the use of a different fit statistics, which takes into account the
uncertainty of the background measurement. This case is covered by the \code{MapDatasetOnOff}
and \code{SpectrumDatasetOnOff} classes, which use the \emph{WStat}~\citep{WStat} statistic.

@@

\subsection{gammapy.makers}
\label{ssec:gammapy-makers}
%
\begin{figure}
        \small
        %Added by TeX Support
    %\import{code-examples/generated/}{gp_makers}
        \caption{
        Using \code{gammapy.makers} to reduce DL3 level data into a
                \code{MapDataset}. All \code{Maker} classes represent 
                a step in the data reduction process. They take
        the configuration on initialization of the class. They 
                also consistently define \code{.run()} methods, which take
                a dataset object and optionally an \code{Observation} 
                object. In this way, \code{Maker} classes can be chained
                to define more complex data reduction pipelines. The output
                of the code example is shown in Figure~\ref{fig:code_example_gp_makers}.
    }
        \label{fig*:minted:gp_makers}
\end{figure}
%
The \code{gammapy.makers} sub-package contains the various classes and functions required
to process and prepare \gammaray data from the DL3 to the DL4.
The end product of the data reduction process is a set of binned counts,
background exposure, psf and energy dispersion maps at the DL4 level, bundled
into a \code{MapDataset} object.
The \code{MapDatasetMaker} and \code{SpectrumDatasetMaker} are
responsible for this task for three- and 1D analyses, respectively (see Figure~\ref{fig*:minted:gp_makers}).

@@

\begin{figure}
        \small
        %Added by TeX Support
        %\import{code-examples/generated/}{gp_stats}
        \caption{
        Using \code{gammapy.stats} to compute statistical quantities
        such as excess, significance and asymmetric errors
        from counts based data. The data array such as \code{counts}, \code{counts\_off}
                and the background efficiency ratio \code{alpha} are passed on initialization
        of the \code{WStatCountsStatistic} class. The derived quantities
        are then computed dynamically from the corresponding class
        attributes such as \code{stat.n\_sig} for the excess
                and \code{stat.sqrt\_ts} for the significance.
                The output of the code example is shown in Figure~\ref{fig:code_example_gp_stats}.
    }
        \label{fig*:minted:gp_stats}
\end{figure}

@@

\begin{figure}
        \small
        %Added by TeX Support
        %\import{code-examples/generated/}{gp_models}
        \caption{Using \code{gammapy.modeling.models} to define a source model with a
    spectral, spatial and temporal component. For convenience the model
    parameters can be defined as strings with attached units. The spatial model
    takes an additional \code{frame} parameter which allow users to define
    the coordinate frame of the position of the model. The output
        of the code example is shown in Figure~\ref{fig:code_example_gp_models}.
    }
        \label{fig*:minted:gp_models}
\end{figure}

@@

\begin{figure}
        \small
        %Added by TeX Support
        %\import{code-examples/generated/}{gp_estimators}
        \caption{Using the \code{TSMapEstimator} object from \code{gammapy.estimators} to compute a
         flux, flux upper limits and TS map. The additional parameters \code{n\_sigma}
        and \code{n\_sigma\_ul} define the confidence levels (in multiples of the normal distribution width)
        of the flux error and flux upper limit maps respectively. The output
                of the code example is shown in Figure~\ref{fig:code_example_gp_estimators}.
    }
    \label{fig*:minted:gp_estimators}
\end{figure}

@@

\begin{figure}
        \small
        %Added by TeX Support
        %\import{code-examples/generated/}{gp_catalogs}
        \caption{Using \code{gammapy.catalogs} to access the underlying model, flux points and
                light-curve from the \fermi 4FGL catalog for the blazar PKS 2155-304. The output
                of the code example is shown in Figure~\ref{fig:code_example_gp_catalogs}.
        }
        \label{fig*:minted:gp_catalogs}
\end{figure}

%\subsection{gammapy.utils}
%\label{ssec:gammapy-utils}
%Utility functions...

@@

\begin{figure}[!ht]
        \small
        %Added by TeX Support
        %\import{code-examples/generated-output/}{gp_data}
        \caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_data}.}
        \label{fig:code_example_gp_data}
\end{figure}

\begin{figure}[!ht]
        \small
        %Added by TeX Support
        %\import{code-examples/generated-output/}{gp_datasets}
        \caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_datasets}.}
        \label{fig:code_example_gp_datasets}
\end{figure}

\begin{figure}[!ht]
        \small
        %Added by TeX Support
        %\import{code-examples/generated-output/}{gp_maps}
        \caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_maps}.}
        \label{fig:code_example_gp_maps}
\end{figure}

\begin{figure}[!ht]
        \small
        %Added by TeX Support
        %\import{code-examples/generated-output/}{gp_stats}
        \caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_stats}.}
        \label{fig:code_example_gp_stats}
\end{figure}

@@

\begin{figure}[!ht]
        \small
        %Added by TeX Support
        %\import{code-examples/generated-output/}{gp_models}
        \caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_models}.}
        \label{fig:code_example_gp_models}
\end{figure}

>>>>

\author{
        Axel Donath \thanks{Mail inquiries to:
        \href{mailto:GAMMAPY-COORDINATION-L@IN2P3.FR}{GAMMAPY-COORDINATION-L@IN2P3.FR}} \inst{\ref{inst:28}} \and
        Régis Terrier \inst{\ref{inst:20}} \and
        Quentin Remy \inst{\ref{inst:17}} \and
        Atreyee Sinha \inst{\ref{inst:15}} \and
        Cosimo Nigro \inst{\ref{inst:24}} \and
        Fabio Pintore \inst{\ref{inst:26}} \and
        Bruno Khélifi \inst{\ref{inst:20}} \and
        Laura Olivera-Nieto \inst{\ref{inst:17}}\and
        Jose Enrique {Ruiz} \inst{\ref{inst:23}} \and
        Kai Brügge \inst{\ref{inst:10},\ref{inst:11}} \and
        Maximilian Linhoff \inst{\ref{inst:11}} \and
        Jose Louis {Contreras} \inst{\ref{inst:15}} \and
        Fabio Acero \inst{\ref{inst:1}} \and
        Arnau Aguasca-Cabot \inst{\ref{inst:2}, \ref{inst:3}, \ref{inst:4}, \ref{inst:5}} \and
        David Berge \inst{\ref{inst:6}, \ref{inst:7}} \and
        Pooja Bhattacharjee \inst{\ref{inst:8}} \and
        Johannes Buchner \inst{\ref{inst:12}} \and
        Catherine Boisson \inst{\ref{inst:9}} \and
        David {Carreto Fidalgo} \inst{\ref{inst:13}} \and
        Andrew Chen \inst{\ref{inst:14}} \and
        Mathieu {de Bony de Lavergne} \inst{\ref{inst:8}} \and
        José Vinícius {de Miranda Cardoso}\inst{\ref{inst:16}} \and
        Christoph Deil \inst{\ref{inst:17}} \and
        Matthias Fü{\ss}ling \inst{\ref{inst:18}} \and
        Stefan Funk \inst{\ref{inst:19}} \and
        Luca Giunti \inst{\ref{inst:20}} \and
        Jim Hinton \inst{\ref{inst:17}} \and
        Léa Jouvin \inst{\ref{inst:32}} \and
        Johannes King \inst{\ref{inst:30}, \ref{inst:17}} \and
        Julien Lefaucheur \inst{\ref{inst:21}, \ref{inst:20}} \and
        Marianne Lemoine-Goumard \inst{\ref{inst:31}} \and
        Jean-Philippe Lenain \inst{\ref{inst:22}} \and
        Rub{\'e}n L{\'o}pez-Coto \inst{\ref{inst:23}} \and
        Lars Mohrmann \inst{\ref{inst:17}} \and
        Daniel Morcuende \inst{\ref{inst:15}} \and
        Sebastian Panny \inst{\ref{inst:25}} \and
        Maxime Regeard \inst{\ref{inst:20}} \and
        Lab Saha \inst{\ref{inst:15}} \and
        Hubert Siejkowski \inst{\ref{inst:27}} \and
        Aneta Siemiginowska \inst{\ref{inst:28}} \and
        Brigitta M. {Sipőcz} \inst{\ref{inst:29}} \and
        Tim Unbehaun \inst{\ref{inst:19}} \and
        Christopher {van Eldik} \inst{\ref{inst:19}} \and
        Thomas Vuillaume \inst{\ref{inst:8}} \and
        Roberta Zanin \inst{\ref{inst:18}}
}

@@

\begin{figure}
        \small
        \import{code-examples/generated/}{gp_data}
        \caption{
        Using \code{gammapy.data} to access DL3 level data with a \code{DataStore} object.
        Individual observations can be accessed by their unique integer observation id number.
        The actual events and instrument response functions can be accessed
        as attributes on the \code{Observation} object, such as \code{.events}
        or \code{.aeff} for the effective area information. The output
                of the code example is shown in Figure~\ref{fig:code_example_gp_data}.
    }
        \label{fig*:minted:gp_data}
\end{figure}
%

@@

\begin{figure}
        \small
        \import{code-examples/generated/}{gp_maps}

@@

\subsection{gammapy.datasets}
\label{ssec:gammapy-datasets}
%
\begin{figure}
        \small
        \import{code-examples/generated/}{gp_datasets}
        \caption{
        Using \code{gammapy.datasets} to read existing reduced binned datasets.
        After the different datasets are read from disk they are collected into a
        common \code{Datasets} container. All dataset types have an associated
        name attribute to allow a later access by name in the code. The
        environment variable \code{\$GAMMAPY\_DATA} is automatically resolved
        by \gammapy. The output
                of the code example is shown in Figure~\ref{fig:code_example_gp_datasets}.
    }
        \label{fig*:minted:gp_datasets}
\end{figure}
%
The \code{gammapy.datasets} sub-package contains classes to bundle
together binned data along with the associated models and likelihood function, which
provides an interface to the \code{Fit} class (Sec \ref{sssec:fit}) for
modeling and fitting purposes. Depending upon the type of analysis and the
associated statistic, different types of Datasets are supported. The \code{MapDataset} is
used for combined spectral and morphological (3D) fitting, while spectral 
fitting only can be performed using the \code{SpectrumDataset}.
While the default fit statistics for both of these classes is the \emph{Cash}~\citep{Cash}
statistic, there are other classes which support
analyses where the background is measured from control regions, so called \enquote{off} observations.
Those require the use of a different fit statistics, which takes into account the
uncertainty of the background measurement. This case is covered by the \code{MapDatasetOnOff}
and \code{SpectrumDatasetOnOff} classes, which use the \emph{WStat}~\citep{WStat} statistic.

@@

\subsection{gammapy.makers}
\label{ssec:gammapy-makers}
%
\begin{figure}
        \small
        \import{code-examples/generated/}{gp_makers}
        \caption{
        Using \code{gammapy.makers} to reduce DL3 level data into a
                \code{MapDataset}. All \code{Maker} classes represent 
                a step in the data reduction process. They take
        the configuration on initialization of the class. They 
                also consistently define \code{.run()} methods, which take
                a dataset object and optionally an \code{Observation} 
                object. In this way, \code{Maker} classes can be chained
                to define more complex data reduction pipelines. The output
                of the code example is shown in Figure~\ref{fig:code_example_gp_makers}.
    }
        \label{fig*:minted:gp_makers}
\end{figure}
%
The \code{gammapy.makers} sub-package contains the various classes and functions required
to process and prepare \gammaray data from the DL3 to the DL4.
The end product of the data reduction process is a set of binned counts,
background exposure, psf and energy dispersion maps at the DL4 level, bundled
into a \code{MapDataset} object.
The \code{MapDatasetMaker} and \code{SpectrumDatasetMaker} are
responsible for this task for three- and 1D analyses, respectively (see Figure~\ref{fig*:minted:gp_makers}).

@@

\begin{figure}
        \small
        \import{code-examples/generated/}{gp_stats}
        \caption{
        Using \code{gammapy.stats} to compute statistical quantities
        such as excess, significance and asymmetric errors
        from counts based data. The data array such as \code{counts}, \code{counts\_off}
                and the background efficiency ratio \code{alpha} are passed on initialization
        of the \code{WStatCountsStatistic} class. The derived quantities
        are then computed dynamically from the corresponding class
        attributes such as \code{stat.n\_sig} for the excess
                and \code{stat.sqrt\_ts} for the significance.
                The output of the code example is shown in Figure~\ref{fig:code_example_gp_stats}.
    }
        \label{fig*:minted:gp_stats}
\end{figure}

@@

\begin{figure}
        \small
        \import{code-examples/generated/}{gp_models}
        \caption{Using \code{gammapy.modeling.models} to define a source model with a
    spectral, spatial and temporal component. For convenience the model
    parameters can be defined as strings with attached units. The spatial model
    takes an additional \code{frame} parameter which allow users to define
    the coordinate frame of the position of the model. The output
        of the code example is shown in Figure~\ref{fig:code_example_gp_models}.
    }
        \label{fig*:minted:gp_models}
\end{figure}

@@

\begin{figure}
        \small
        \import{code-examples/generated/}{gp_estimators}
        \caption{Using the \code{TSMapEstimator} object from \code{gammapy.estimators} to compute a
         flux, flux upper limits and TS map. The additional parameters \code{n\_sigma}
        and \code{n\_sigma\_ul} define the confidence levels (in multiples of the normal distribution width)
        of the flux error and flux upper limit maps respectively. The output
                of the code example is shown in Figure~\ref{fig:code_example_gp_estimators}.
    }
    \label{fig*:minted:gp_estimators}
\end{figure}

@@

\begin{figure}
        \small
        \import{code-examples/generated/}{gp_catalogs}
        \caption{Using \code{gammapy.catalogs} to access the underlying model, flux points and
                light-curve from the \fermi 4FGL catalog for the blazar PKS 2155-304. The output
                of the code example is shown in Figure~\ref{fig:code_example_gp_catalogs}.
        }
        \label{fig*:minted:gp_catalogs}
\end{figure}

@@

\begin{figure}[!ht]
        \small
    	\import{code-examples/generated-output/}{gp_data}
        \caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_data}.}
        \label{fig:code_example_gp_data}
\end{figure}

\begin{figure}[!ht]
        \small
        \import{code-examples/generated-output/}{gp_datasets}
        \caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_datasets}.}
        \label{fig:code_example_gp_datasets}
\end{figure}

\begin{figure}[!ht]
        \small
        \import{code-examples/generated-output/}{gp_maps}
        \caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_maps}.}
        \label{fig:code_example_gp_maps}
\end{figure}

\begin{figure}[!ht]
        \small
        \import{code-examples/generated-output/}{gp_stats}
        \caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_stats}.}
        \label{fig:code_example_gp_stats}
\end{figure}

@@

\begin{figure}[!ht]
        \small
        \import{code-examples/generated-output/}{gp_models}
        \caption{Output from the code example shown in Figure~\ref{fig*:minted:gp_models}.}
        \label{fig:code_example_gp_models}
\end{figure}
